Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-10-21 saner/paper.tex
Updates from Overleaf

\usepackage{todo}
\usepackage{amsmath}

@@

\title{Improving Software Maintainability through Automated Refactoring of Code Clones}

\maketitle
\thispagestyle{plain} % This is for page numbers, remove before submit
\pagestyle{plain}

@@

\begin{abstract}
Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code. To remove such anti-patterns, the codebase should be refactored. Many tools aid in the detection process of such duplication problems but fail to determine whether refactoring a duplicate fragment would improve the maintainability.

We address this shortcoming by first analyzing what data should be gathered from an automatically refactored system. We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them. We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system. Based on these results, one could decide which clones would improve system design if refactored. We evaluate our approach over a large corpus of open source Java projects.

@@

\todo{color package}
\begin{table}[H]
\centering
\begin{tabular}{@{}llrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{Total}} \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} \\ \cmidrule(lr){2-3}
 & Same Method & 8,955 &  \\ \midrule
\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & \multirow{5}{*}{20,342} \\ \cmidrule(lr){2-3}
 & Superclass & 2,616 &  \\ \cmidrule(lr){2-3}
 & First Cousin & 1,219 &  \\ \cmidrule(lr){2-3}
 & Common Hierarchy & 720 &  \\ \cmidrule(lr){2-3}
 & Ancestor & 199 &  \\ \midrule
\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & \multirow{4}{*}{20,314} \\ \cmidrule(lr){2-3}
 & External Superclass & 4,525 &  \\ \cmidrule(lr){2-3}
 & External Ancestor & 3,347 &  \\ \cmidrule(lr){2-3}
 & No Indirect Superclass & 1,765 &  \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & \multirow{2}{*}{13,074} \\ \cmidrule(lr){2-3}
 & Same Indirect Interface & 5,552 &  \\ \bottomrule
\end{tabular}
\caption{Number of clone classes per clone relation}
\label{tab:relation}
\end{table}

>>>>

\usepackage{todonotes}
\usepackage{amsmath}

@@

\title{Improving Software Maintainability through Automated Refactoring of Code Clones}
\author{}
\maketitle
\thispagestyle{plain} % This is for page numbers, remove before submit
\pagestyle{plain}

@@

\begin{abstract}
Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code. To remove such anti-patterns, the codebase should be refactored. Many tools aid in the detection process of such duplication problems but do not determine whether refactoring a duplicate fragment would improve the maintainability.

We address this shortcoming by first analyzing what factors influence the maintainability of clones when refactored. We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them. We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system. Based on these results, one could decide which clones would improve system design if refactored. We evaluate our approach over a large corpus of open source Java projects.

@@

\begin{table}[H]
\centering
\begin{tabular}{@{}llrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{Total}} \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} \\ \cmidrule(lr){2-3}
 & Same Method & 8,955 &  \\ \midrule
\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & \multirow{5}{*}{20,342} \\ \cmidrule(lr){2-3}
 & Superclass & 2,616 &  \\ \cmidrule(lr){2-3}
 & First Cousin & 1,219 &  \\ \cmidrule(lr){2-3}
 & Common Hierarchy & 720 &  \\ \cmidrule(lr){2-3}
 & Ancestor & 199 &  \\ \midrule
\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & \multirow{4}{*}{20,314} \\ \cmidrule(lr){2-3}
 & External Superclass & 4,525 &  \\ \cmidrule(lr){2-3}
 & External Ancestor & 3,347 &  \\ \cmidrule(lr){2-3}
 & No Indirect Superclass & 1,765 &  \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & \multirow{2}{*}{13,074} \\ \cmidrule(lr){2-3}
 & Same Indirect Interface & 5,552 &  \\ \bottomrule
\end{tabular}
\caption{Number of clone classes per clone relation}
\label{tab:relation}
\end{table}
